Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-03-02 manuscript/tables&figures.Rmd
update table 3 header

```{r, Table 3, eval=TRUE, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
table3 <- read.csv("tables_figures/table3_species_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
table3[8,8] <- paste0(table3[8,8], footnote_marker_symbol(1))
kable(table3, format = "latex", booktabs=TRUE, caption = "Table 3. Overview of analyzed species, their productivity in the plot, numbers and sizes sampled, and traits.  Given are DBH mean and range of cored trees, the number of cores represented by each crown position of each species, and mean hydraulic trait measurements.", escape=FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," ", "DBH (cm)" = 2, "species traits (mean +/- sd)" = 5)) %>%
  #kable_styling(bootstrap_options = "striped", full_width = FALSE)
kableExtra::footnote(symbol = c("Semi-ring porosity is intermediate between ring and diffuse. We group it with diffuse-porous species for more even division of species between categories."), footnote_as_chunk = FALSE)
```

>>>>

```{r, Table 3, eval=TRUE, echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
table3 <- read.csv("tables_figures/table3_species_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
table3[8,8] <- paste0(table3[8,8], footnote_marker_symbol(1))
kable(table3, format = "latex", booktabs=TRUE, caption = "Table 3. Overview of analyzed species, listed in order of their relative contributions to woody stem productivity ($ANPP_{stem}$) in the plot, along with numbers and sizes sampled, and species traits.", escape=FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," ", "DBH (cm)" = 2, "species traits (mean +/- sd)" = 5)) %>%
  #kable_styling(bootstrap_options = "striped", full_width = FALSE)
kableExtra::footnote(symbol = c("Semi-ring porosity is intermediate between ring and diffuse. We group it with diffuse-porous species for more even division of species between categories."), footnote_as_chunk = FALSE)
```
